Comparing R packages for calculation of persistent homology

### 2020-01-31 tdabench-paper/tdabench.Rmd
shortened wording
shortened sentence
removed unnecessary subheading, shortened text

\subsubsection{Prototype/Canonical dataset (Torus)}
The torus point cloud is a classical shape used to demonstrate persistent homology calculations. 
A persistent homology calculation of a uniformly distributed torus would reveal a large 1 dimensional feature representing the middle circle of the torus. There would also be a large 2 dimensional feature representing the inner cavity of the torus. 
In figure \ref{fig:tor}, we calculated up to 2 dimensional features of torus 3d points cloud for an increasing number of points across all TDA libraries.

>>>>

Computing persistent homology of a canonical torus grants quick insight into efficiency of each library (Figure \ref{fig:tor}).
Calculating persistent homology of points distributed on a torus should reveal a single 1-dimensional feature representing the middle circle of the torus. There would also be a large 2 dimensional feature representing the inner cavity of the torus. 
In figure \ref{fig:tor}, we calculated up to 2 dimensional features of torus 3d points cloud for an increasing number of points across all TDA libraries.
